TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-19 paper/draft.tex
add model ref

The \apogee\ survey is a high resolution (R$\sim$22,500), H-band (1.5-1.7$\mu$m), multi-epoch survey which has observed over 250,000 stellar spectra up to its fourteenth data release (DR14; \citealt{Abolfathi:2017}). Fundamental parameters for each of these stars are estimated by the \apogee\ Stellar Parameter and Chemical Abundances Pipeline (ASPCAP; \citealt{Perez:2016}), which employs a $\chi^2$ fitting procedure using the \textsl{FERRE} code to fit radiative transfer models and determine atmospheric parameters, 15 chemical abundances and micro-turbulence parameters ($\teff$, $\logg$, $\feh$, [$\alpha$/M], [C/M], [N/M]; \citealt{Meszaros:2012}). For low temperatures ($2800<\teff<3500$\,K), the pipeline uses \textsl{MARCS} plane-parallel/spherical models \citep{Gustafsson:2008}, and for higher temperatures ($\teff\geq3500$\,K) \textsl{ATLAS9} \citep{Castelli:2004} plane-parallel models are used.

@@

A number of studies out of the M dwarf ancilliary survey have already been conducted towards measuring reliable fundamental atmospheric parameters and kinematic measurements using spectral synthesis of atmospheric model grids. 
These studies include \citealt{Desphande:2013} and \citealt{Gilhool:2018} which have studied the radial and rotational kinematics for 700+ sources,
\citealt{Souto:2017} and \citealt{Souto:2018} which have modeled three exoplanet hosting M dwarfs (Kepler-138, Kepler-168 and Ross-128), determining $\teff$/$\logg$/metallicity + 13 elemental abundances,
\citealt{Rajpurohit:2018} which tested BTSettl model grids \citep{Allard:2012} on 45 M dwarfs to estimate $\teff$/$\logg$/metallicity,
and \citealt{Skinner:2018} which has identified and measured mass ratios and radial velocities for 44 M dwarf spectroscopic binaries.
This work complements existing studies by producing model-independent catalog of spectroscopic temperatures and metallicites to test against model predictions for the entire \apogee\ M dwarf sample, which we quantify to contain at least 10,000 sources to date (DR14).

>>>>

The \apogee\ survey is a high resolution (R$\sim$22,500), H-band (1.5-1.7$\mu$m), multi-epoch survey which has observed over 250,000 stellar spectra up to its fourteenth data release (DR14; \citealt{Abolfathi:2017}). Fundamental parameters for each of these stars are estimated by the \apogee\ Stellar Parameter and Chemical Abundances Pipeline (ASPCAP; \citealt{Perez:2016}), which employs a $\chi^2$ fitting procedure using the FERRE code to fit radiative transfer models and determine atmospheric parameters, 15 chemical abundances and micro-turbulence parameters ($\teff$, $\logg$, $\feh$, [$\alpha$/M], [C/M], [N/M]; \citealt{Meszaros:2012}). For low temperatures ($2800<\teff<3500$\,K), the pipeline uses MARCS plane-parallel/spherical models \citep{Gustafsson:2008}, and for higher temperatures ($\teff\geq3500$\,K) ATLAS9 \citep{Castelli:2004} plane-parallel models are used.

@@

A number of studies out of the M dwarf ancilliary survey have already been conducted towards measuring reliable fundamental atmospheric parameters and kinematic measurements using spectral synthesis of atmospheric model grids. 
These studies include \citealt{Desphande:2013} and \citealt{Gilhool:2018} which have studied the radial and rotational kinematics for 700+ sources,
\citealt{Souto:2017} and \citealt{Souto:2018} which have modeled three exoplanet hosting M dwarfs (Kepler-138, Kepler-168 and Ross-128), determining $\teff$/$\logg$/metallicity + 13 elemental abundances,
\citealt{Rajpurohit:2018} which tested BT-Settl \citep{Allard:2012} and MARCS \citep{Gustafsson:2008} model grids on 45 M dwarfs to estimate $\teff$/$\logg$/metallicity,
and \citealt{Skinner:2018} which has identified and measured mass ratios and radial velocities for 44 M dwarf spectroscopic binaries.
This work complements existing studies by producing model-independent catalog of spectroscopic temperatures and metallicites to test against model predictions for the entire \apogee\ M dwarf sample, which we quantify to contain at least 10,000 sources to date (DR14).
